Supplementary Information

### 2015-06-22 manuscript/supplement.tex
updated figures and compiled

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}
\medskip$^2$Department of Biology\\Life Science Centre\\
Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
Halifax, NS B3H 4R2\\Canada\\}

\begin{document}
\maketitle
\baselineskip=8.5mm
% \linenumbers

\vspace{0.4 in}
\beginsupplement
\begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

@@

\begin{figure}[H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}

>>>>

\begin{document}

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\
\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\}

\maketitle
\baselineskip=8.5mm
% \linenumbers

\vspace{0.4 in}
\beginsupplement
% \begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}

\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN}% your .bib file(s)
